\documentclass{article}
\usepackage{html}
\usepackage[latin1]{inputenc}
%Párrafos
\setlength{\parskip}{1pc}

\begin{document}

% Title Page
\title{ITK Weighted Local Stats Gui}
\author{Karl Krissian \& Sara Arencibia}
\thanks{
Grupo de Imagen, Tecnolog\'ia M\'edica y Televisi\'on (GIMET)\\
Universidad de Las Palmas de Gran Canaria\\
email: krissian@dis.ulpgc.es darkmind@gmail.com
}


\maketitle

\begin{abstract}
Script to compute probability of belonging to a structure based on an intensity mapping of the local statistics of the image intensity (local mean and local standard deviation)
\end{abstract}


\section{Quick Start}

The different steps for obtaining the Weighted Local Stats are:
\begin{enumerate}
  \item Select and load the input image.
  \item Select and load the wights input image.
  \item Select the dimension of the image (2D or 3D).
  \item Select the prefix for the output image name.
  \item Select the size of the window.
  \item Select the minimal weight.
  \item Run the filter.
  \item Display the result.
\end{enumerate}

\section{Interface tabs}

The interface is divided into several pages.

\subsection{\emph{Init} page}

Select and load the input image.
Select and load the weights image.
The {\bf Dimension} parameter allows to set the dimension of the image (2D or 3D).

\subsection{\emph{Param} page}

\begin{enumerate}
  \item Select the size of the window to compute local mean.
  \item Select the minimal weight to compute weighted local standard deviation of intensity.
  \item Run the filter.
  \item Display the result.
\end{enumerate}


\subsection{\emph{Help} page}
This help.

\end{document}          
